Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-09-26 paper2_JNLS/paper.tex
NM

In this way, the statistical theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover certain statistical features of the system at hand. We remind the reader that KdV is asymptotically valid only for large spatial scales, and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV are on equal footing as far as physical realism -- a more accurate framework would require either model closure to capture the small scale physics or else direct numerical simulation of the Euler equations. Where differences exist between KdV and TKdV, therefore, it is unclear {\em a priori} which model, if either, more closely resembles reality. This situation, of course, underscores the importance of controlled laboratory experiments.
}

>>>>

In this way, the statistical theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover certain statistical features of the system at hand. We remind the reader that KdV is asymptotically valid only for large spatial scales, and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV are on equal footing as far as physical realism --- a more accurate framework would require either model closure to capture the small scale physics or else direct numerical simulation of the Euler equations. Where differences exist between KdV and TKdV, therefore, it is unclear {\em a priori} which model, if either, more closely resembles reality. This situation, of course, underscores the importance of controlled laboratory experiments.
}
